\huge Tor's Usability for Censorship Circumvention

### 2016-05-04 pets2017-paper/pets2017-paper.tex
Dave's suggestions.
-rearrange the results section: rate of success, time to success, and active time
-add detail about why people failed, showing tor log button and log lines
-added which users failed how into the failed section
-deleted claims which were subjective
-added clarifications on calculations and points being made
-additional textual changes

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

@@

@@

The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen. Participants using the new interface and old interface spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively. We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen, which were present in both versions of the interface.

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
	\end{tabular}
\caption{Fraction of time spent on each screen.
Participants spent most of their time on the progress screen, waiting.
Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
although none of the censorship environments required a proxy.
Participants spent less time on the proxy screen
in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
\label{table:overall_time}
\end{table}

Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection. We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen. This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting. However, this behavior was equally likely in the new and old interface conditions.

The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$), while maintaining the same probability for success for the user. We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)

\subsubsection{Time to Success} 
Although the median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}), this difference is not statistically significant. The level of censorship had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40:08
for the purpose of computing the median.
}
\label{fig:time_to_success_clamped}
\end{figure}

In our experiment, participants had 40 minutes to circumvent censorship. Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time. Participants were less and less likely to succeed as time went on. Users in the wild will likely not be motivated to configure their connection for 40 minutes. If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect. Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect. Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment. We propose ideas on how to achieve this in section~\ref{recommendations}.

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
}
\label{fig:time_to_success_ecdf}
\end{figure}

\subsubsection{Rate of Success} 
Five more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network. Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. However, this does suggest that users are equally likely to succeed with the new interface. 
% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)

Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination. Note that only four of the default bridges were used to connect successfully for the first time. Users avoid making decisions when a recommendation is given and tend to avoid or fail with more advanced options. Participants who were in environments where the recommended bridge (obfs3) worked did not successfully configure another bridge. Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.

We believe that our change to add advice on what to try next on error messages (such as try the connection again, reconfigure your bridge settings, or try without a proxy) would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment. That participant, who used the new interface, saw that the bridge configuration was the source of the error, and heeded the interface's advice to reconfigure the bridge options. But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results. The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back to adjusted them), but this behavioral change did not have a statistically significant impact on success rates. We added pre-preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not read this advice.

@@

\subsubsection{Observations}
These are general observations made from our data set of participants, which may or may not be representative of the Tor user base.\\

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays and try the easy option of connecting directly to the Tor network first, leaking that they are connecting to Tor on the network.  81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface. It's critical to note that the participants did not believe the interface when it informed them that they did not need a proxy.

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} Users believed that they needed proxies to connect. This confusion prevented users from configuring their bridges correctly. Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface. Participants in the old interface who did not receive feedback spent 63\%.

% impacts of giving people advice on which transport to choose.
\item {\bfseries Certain transports were chosen with high probability.}
Of those who tried an obfs3 bridge and failed, 
66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge. We suspect that flashproxy was a popular choice because it is listed first in the drop-down menu. Many bridges listed at the end of the drop-down menu were not chosen.

%error messages
\item {\bfseries There were (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message. Error messages are intended to appear after a timeout. There were warnings, but those warnings went largely unnoticed by our participants. Across both versions of the interface, only one participant ever saw an error message.

We are unable to state the efficacy of our attempts to make instructive and understandable error messages due to lack of data. We do not understand why users with the new interface choose to configure proxies after explicitly being told that they do not need one. We notice that users in the new interface were more likely to chose meek bridges. 10 users in the new interface chose a meek-bridge as their second bridge, whereas only 5 users in the old interface did. However, we cannot say if this can be attributed to the advice we added on the bridge configuration screen, due to the small sample size.

\subsubsection{Reasons for Failure} 
Failure is common. 20\% (21 of 116) of participants failed entirely. 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed. Reasons for failure were determined by a combination of log processing (i.e. how much time was spent on a particular screen) and video observation (i.e. observing what they searched for online). \\

@@

@@

\begin{description}
\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor. Automating the configuration process thereafter will have no increase in risk, but can help a majority of users; 64\% of participants who failed their first attempt. Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time configuring a proxy. Only a small fraction of the Internet population requires a proxy to connect to the Internet. Hiding the proxy screen by default and only showing it after it has been detected as necessary can focus user efforts on configuring bridges.
\item {\bfseries Be explicit about recommendations.} Being explicit about the order in which a user should choose bridges will result in higher rates of success and lessen cognitive load on the user. Most participants followed recommendations about which bridge to choose, and many did not know what to do after the recommended bridge failed. 
\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
\item{\bfseries Have a user-tolerant auto-responder.} Having the auto-responder default respond with bridges or catching common errors (such as typing ``get bridges'' in the subject line) can help those who need custom bridges. 
\end{description}

>>>>

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
%\small
%\begin{itemize}
%\renewcommand{\labelitemi}{$\circ$}
%\item Connect with provided bridges\\
%Transport type:
%\begin{itemize}
%\item flashproxy
%\item fte
%\item fte-ipv6
%\item meek-amazon
%\item meek-azure
%\item meek-google
%\item obfs3 (recommended)
%\item obfs4
%\item scramblesuit
%\end{itemize}
%\item Enter custom bridges\qquad\fbox{Help}\\
%\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

@@

\subsubsection{Rate of Success} 
50 of 58 (86\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. This suggests that users no less likely to succeed with the new interface. 
% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{warning.png}
\caption{
A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
which appears silently and does not interrupt the progress bar. 
This warning was generated by entering in syntactically correct but invalid proxy settings,
a mistake that prevents users from ever connecting to the Tor network. 
Users are never directly notified of this error through an error message or a timeout message.
Our participants made this error during our experiments, along with others that they were not notified about. 
}
\label{fig:warning}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=.5\textwidth]{log-messages.png}
\caption{
The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
These log lines were the result of entering in syntactically correct but invalid proxy settings,
a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
}
\label{fig:warning_log}
\end{figure}

We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment. The old interface warned users on some mistakes (i.e. entering in a syntactically correct but invalid proxy settings) rather than displaying an error message. When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}). To see the log messages, users must click on the button, open up a text editor, and paste the log messages. The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).

That participant was using the new interface and was told that the bridge configuration was the source of the error. The participant heeded the interface's advice to reconfigure the bridge options. But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results. The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.

We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure. Of the 76 participants that failed to connect on the first attempt, 15 of 36 participants with the new interface and 13 of 38 participants with the old interface went back to the bridge screen and chose another hard-coded bridge. 10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim that this is a direct result of our advice.

Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.We only consider the first successful connection since many of our curious participants tried many different settings to investigate if they will work, even after they had completed the task. Recall E1 does not require users to configure a bridge, E2 requires users to configure any bridge, and E3 requires users to configure a meek or custom bridge. Note that only four of the hard-coded bridges were used to connect successfully for the first attempt were the recommended bridge and the required bridges to succeed in E3.

Our participants did not optionally configure a bridge in E1 or configure a non-recommended bridge in E2. This suggests that users will not configure optional components or deviate from the recommended settings unless necessary. If the intent of the recommendation is to get as many users as possible to use the recommended bridge, this is a positive result. If the intent of the recommendation is to give pointers when users are stuck but allow the users to make their own bridge choices to diversify active transports, this is a negative result.

Only two participants chose to configure a custom bridge. Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result. Appendix~\ref{failed-participants} shows the malformed requests. These two participants failed to connect to the Tor network.

\subsubsection{Time to Success} 
The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}). However, this difference is not statistically significant. The level of censorship had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})

\begin{figure}[t]
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40:08
for the purpose of computing the median.
}
\label{fig:time_to_success_clamped}
\end{figure}

In our experiment, participants had 40 minutes to circumvent censorship. Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time. In practice, faster time to completion would mean more users will succeed, since users will give up after a while. Users in the wild will likely not be motivated to spend 40 minutes trying to configure Tor. If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect. Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect. Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment. We propose ideas on how to achieve this in section~\ref{recommendations}.

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Logs show that participants spent 64\% of their overall time at the progress screen. 
Participants using the new interface and old interface spent approximately the same amount of absolute time on the progress screen (359 minutes versus 339 minutes, respectively). 
Table ~\ref{table:overall_time} shows the percentage of time spent on each screen,
computed by the total number of minutes all participants spent on each screen.

We believe participants spent a long time on the progress screen for a combination of reasons. Even with correct configurations, the bootstrap process can take up to two minutes. With incorrect settings, we suspect that participants waited because the interface instructs them ``wait a couple minutes.'' A lack of error messages and timeouts on the progress screen, also caused some users to wait indefinitely.

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  5\% & 17\% & 6\% & 0\% & 64\% \\
	E1-NEW & 34\% & 4\% & 6\% & 1\% & 50\% \\
	E1-OLD & 23\% & 35\% & 9\% & N/A & 21\% \\
	E2-NEW & 5\% & 4\% & 4\% & 1\% & 80\% \\
	E2-OLD & 4\% & 22\% & 4\% & N/A & 66\% \\
	E3-NEW & 6\% & 7\% & 4\% & 1\% & 70\% \\
	E3-OLD & 4\% & 25\% & 9\% & N/A & 60\% \\
	\end{tabular}
\caption{Fraction of time spent on each screen, 
computed by the total number of minutes all participants spent on each screen. 
Participants spent most of their time on the progress screen.
Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
although none of the censorship environments required a proxy.
Participants spent less time on the proxy screen
in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
\label{table:overall_time}
\end{table}

Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection. We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap. This is a simplified notion active configuration time. Some participants searched for help on the web after exiting the interface or on the progress screen.

The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$). We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)

@@

\subsubsection{Reasons for Failure} 
Failure is common. 20\% (21 of 116) of participants were not able to successfully connect to Tor. 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed. Reasons for failure were determined by a combination of log processing (i.e. configuration settings on attempts) and video observation (i.e. observing what they searched for online). \\

@@

\subsubsection{Observations}
We noticed several patterns in the behavior of our participants. These may or may not apply to the Tor user base.\\

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.} Users try the easy option of connecting directly to the Tor network first. This leaks to network eavesdroppers leaking that they are connecting to Tor.  81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly. Participants with the new interface (which explicitly states that they did not need a proxy) spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface. Participants in the old interface spent 63\% of their time on the proxy screen. We do not understand why users with the new interface chose to configure proxies after explicitly being told that they do not need one.

% impacts of giving people advice on which transport to choose.
\item {\bfseries The interface has a large influence on the bridges chosen.}
Participants in E3 were required to choose a particular subset of hard-coded bridges, none of which was the default bridge. After the default bridge, the most chosen bridge was the one listed first in the drop-down menu. Many bridges listed at the end of the drop-down menu were not chosen. We tried to help users by providing instructions on which bridges to choose if the default fails, but it is unclear if this advice helped. 66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.

%error messages
\item {\bfseries People saw (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message. Error messages are intended to appear after a timeout. There were warnings, but those warnings went largely unnoticed by our participants. Across both versions of the interface, only one participant ever saw an error message. We tried to make error messages more instructive and understandable, bu since participants in our experiment did not encounter error messages, we cannot evaluate their efficacy.

@@

\begin{description}
\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor. Automating the configuration process thereafter will have no increase in risk, but can help a majority of users. This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 64\% of participants who failed their first attempt. Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time configuring a proxy. Only a small fraction of the Internet population requires a proxy to connect to the Internet. Hiding the proxy screen by default and only showing it after it has been detected as necessary can focus user efforts on configuring bridges.
\item {\bfseries Be explicit about recommendations.} Being explicit about the order in which a user should choose bridges will result in higher rates of success and lessen cognitive load on the user. Most participants followed recommendations about which bridge to choose, and many did not know what to do after the recommended bridge failed. 
\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
\item{\bfseries Have a user-tolerant auto-responder.} Having the auto-responder default respond with bridges or catching common errors (such as typing ``get bridges'' in the subject line) can help those who need custom bridges. 
\end{description}
